Preprocessing: filtering

### 2022-08-14 analysis/filtering.Rmd
add missing notes removal
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extra, include = FALSE}
dt_error_onset$CorrectionNr <- NA

@@

# export csv
fwrite(dt_correct_onset_2, file = here("filtered", "dt_correct_onset_2.txt"))
```

@@

```{r extra, include = FALSE}
dt_error_offset$CorrectionNr <- NA

@@

# export csv
fwrite(dt_correct_offset_2, file = here("filtered", "dt_correct_offset_2.txt"))
```

>>>>

```{r extra-onset, include = FALSE, eval = FALSE}
dt_error_onset$CorrectionNr <- NA

@@

# export csv
fwrite(dt_correct_onset_2, file = here("filtered", "dt_correct_onset_2.txt"))
fwrite(error_extra_onset, file = here("filtered", "error_extra_onset.txt"))
```

```{r}
error_extra_onset <- fread(here("filtered/error_extra_onset.txt"))
error_extra_onset
```

@@

```{r extra-offset, include = FALSE, eval = FALSE}
dt_error_offset$CorrectionNr <- NA

@@

# export csv
fwrite(dt_correct_offset_2, file = here("filtered", "dt_correct_offset_2.txt"))
fwrite(error_extra_offset, file = here("filtered", "error_extra_offset.txt"))
```

```{r}
error_extra_offset <- fread(here("filtered/error_extra_offset.txt"))
error_extra_offset
```

## Missing notes
1) Onset

```{r missing-onset, include = FALSE, eval = FALSE}
error_missing_onset <- dt_error_onset[Reason == "Missing Notes"]

dt_correct_onset_3 <- data.table()
for (row in 1:nrow(error_missing_onset)){
  current <- dt_onset[SubNr == error_missing_onset$SubNr[row] & TrialNr == error_missing_onset$TrialNr[row]]
  diff <- abs(nrow(dt_ideal) - nrow(current))
  if (diff < 5){
    # insert NA row
    current <- insert_na(current, dt_ideal)
    print(sprintf("SubNr: %s, TrialNr: %s", unique(current$SubNr), unique(current$TrialNr)))
    print("----- Correction check -----")
    current <- edit(current, dt_ideal)
    decision <- menu(c("y", "other"), title = "Save the current data?")
    if (decision == 1){
      error_missing_onset$CorrectionNr[row] <- diff
      dt_correct_onset_3 <- rbind(dt_correct_onset_3, current[, -c(5:6)])
    } else if (decision == 2){
      error_missing_onset$CorrectionNr[row] <- readline(prompt = "Reason?: ")
    }
  } else {
    error_missing_onset$CorrectionNr[row] <- "Check individually"
  }
}

# export csv
fwrite(dt_correct_onset_3, file = here("filtered", "dt_correct_onset_3.txt"))
fwrite(error_missing_onset, file = here("filtered", "error_missing_onset.txt"))
```

```{r}
error_missing_onset <- fread(here("filtered/error_missing_onset.txt"))
error_missing_onset
```

```{r missing-offset, include = FALSE}
error_missing_offset <- dt_error_offset[Reason == "Missing Notes"]

dt_correct_offset_3 <- data.table()
for (row in 1:nrow(error_missing_offset)){
  current <- dt_offset[SubNr == error_missing_offset$SubNr[row] & TrialNr == error_missing_offset$TrialNr[row]]
  diff <- abs(nrow(dt_ideal) - nrow(current))
  if (diff < 5){
    # insert NA row
    current <- insert_na(current, dt_ideal)
    print(sprintf("SubNr: %s, TrialNr: %s", unique(current$SubNr), unique(current$TrialNr)))
    print("----- Correction check -----")
    current <- edit(current, dt_ideal)
    decision <- menu(c("y", "other"), title = "Save the current data?")
    if (decision == 1){
      error_missing_offset$CorrectionNr[row] <- diff
      dt_correct_offset_3 <- rbind(dt_correct_offset_3, current[, -c(5:6)])
    } else if (decision == 2){
      error_missing_offset$CorrectionNr[row] <- readline(prompt = "Reason?: ")
    }
  } else {
    error_missing_offset$CorrectionNr[row] <- "Check individually"
  }
}

# export csv
fwrite(dt_correct_offset_3, file = here("filtered", "dt_correct_offset_3.txt"))
fwrite(error_missing_offset, file = here("filtered", "error_missing_offset.txt"))
```

```{r}
error_missing_offset <- fread(here("filtered/error_missing_offset.txt"))
error_missing_offset
```
